---
title: "Mama study - 2nd"
author: "Kính"
output:
    html_document:
        toc: true
        toc_float: true
        code_folding: hide
always_allow_html: true
---

```{r setup, include=F}
source("/Users/knguyen/Documents/libs.r")
select <- dplyr::select
```

```{r readdata}
d <- readxl::read_excel(here("./2_23_Amandla mama data_.xlsx"), col_types = "text")
d %<>%
    rename(
        id = `Participant number`,
        rid = `Randomisation code`,
        agec = Age,
        area = `Facility`,
        video = `Did you receive the videos?`,
        video_any = `Did you see the videos from anyone?2`,
        momconnect = `Are you enrolled on MomConnect?`,
        age = `How   old are you?`,
        edu = `What is the highest standard or grade you have completed at school?`,
        race = `With which race group do you identify?`,
        nat = `What nationality are you?`,
        work = `Have you worked to earn money in the last 12 months?`,
        earn = `How much do you earn per month, before tax, including benefits?`,
        partner = `Do you have a partner?`,
        reli = `What is your religion, if you have one?`,
        k9_F = `Kangaroo mother care should be avoided because it makes breastfeeding difficult`,
        k10_T = `Drinking breastmilk prevents infections in a baby`,
        k11_T = `Breastmilk alone provides enough nutrition until babies are 6 months old`,
        k12_F = `Babies should be given water or cooled tea in addition to breastmilk when it is hot outside`,
        k13_F = `Formula feeding is healthier for babies than breastfeeding if mothers can afford it`,
        k14_F = `Babies under six months should be given muti if recommended by a sangoma`,
        k15_F = `Pregnant mothers should avoid fruits because it will be too acidic for the baby`,
        k16_F = `It’s okay to drink alcohol when pregnant because it relaxes the mother`,
        k17_T = `Iron is found in green vegetables as well as meat`,
        k18_T = `It is important for pregnant women to get enough nutrients in their meals`,
        k19_T = `Beans are an excellent source of protein`,
        k20_F = `Eggs are an excellent source of starch`,
        k21_F = `Women don’t need to care for themselves during pregnancy`,
        k22_T = `Pregnant women should visit the clinic regularly to check for infections that can affect the baby`,
        k23_F = `A pregnant woman should not eat healthy food if the baby is growing well`,
        k24_T = `Immunization help to protect newborn babies from getting sick`,
        k25_F = `Immunization are dangerous for newborn babies and should be delayed until the child is older`,
        k26_F = `Difficulty sleeping during late pregnancy is a danger sign`,
        k27_T = `Severe headaches during late pregnancy are danger signs`,
        k28_T = `Feeling your baby kick is normal during late pregnancy`,
        k29_F = `Bleeding from the vagina is normal during late pregnancy`,
        k30_F = `When a newborn baby loses some weight in the first week it is a danger sign`,
        k31_T = `When a newborn has a fever in the first week it is a danger sign`,
        k32_F = `When a newborn cries a lot at night, it is a danger sign.`,
        k33_F = `When a newborn has black stools in the first week, it is a danger sign`,
        k34_T = `Pregnant women should visit the clinic regularly, even if they feel fine`,
        k35_T = `Pregnant women should exercise`,
        k36_F = `Newborn babies can be given porridge to help them gain weight and sleep better.`
    ) %>%
    select(1:43)
```

CHANGES:

- Group 1 individual in no formal education to primary school

Some issues:

- [x] 8 have repeated IDs with different records --> assume they are different
- [x] 2 with missing all the answer to knowledge --> removed
- [x] no id 73, but two 28, it seems the second one is 73 based on video category

**Statistical analysis**

The questions were scored by allocating +1 point for each correct answer and 0
points if participants answered incorrectly or if they answered: “I don’t know.”
The sum score is thus can be considered as discrete counts with bounded value at
the total number of questions (28 in the case of general question, 21 in the
case of subset of questions relevant to the video, and varied in subgroup
analyse). Thus, we used the Beta-Binomal distribution which can account for
over- and under-dispersion and the fact that the distribution is bounded. The
distribution outperformed the Poisson and Negative Binomal when compared to the
emprical distribution (Figure X - Appendix).

We compared demographic variables distribution between the trial arms with
Chi-square or exact Fisher test as appropriated. We conducted multiple
regression analyses to explore the effect on the overall knowledge scores of the
SAS Intervention group with intention to treat approach. We also conducted the
analyses by four topic sub-groups within the knowledge questionnaire. The topic
sub-groups include breastfeeding, newborn care, pregnancy care, and
breastfeeding and newborn care. The regression models were adjusted for the
demographics variables including age, sex, education level, as well as whether
the mother was enrolled in the MomConnect program. The models were fitted using
Bayesian inference framework using the statistical program R 4.0.2. We reported
the IQR and 95% uncertainty interval of the posterior distribution of the parameter estimates as well as the marignal estimates of the transformed original score to aid interpretion.

There were 11 individuals with missing data in one of the 28 knowledge
questions; in these cases, we applied imputation to randomly sampling the
questions’ response and conducted analyses on the imputed samples to check
sensitivity of the results against those missing values. Finally, we analyzed
the maternal satisfaction data by calculating a mean score for each of the
different subjective user satisfaction questions, to capture maternal
satisfaction related to use of the SAS videos.

```{r meta_group}
read.csv("cate.csv") %>%
    mutate(
        q = paste0("k", q),
        across(pc:bfnc, as_numeric)
    ) %>%
    allot(cate)

# PP or ITT
pp_id <- c(8, 28, 80, 300, 342, 382, 49, 36, 252, 75, 73, 111)
```

```{r recoding_answer}
d %>%
    filter(!id %in% c(98, 103)) %>% # no answers
    mutate(
        id_ = 1:n(), 
        id = if_else(id_ == 15, '73', id),
        pp = video,
        itt = if_else(id %in% pp_id, 'Yes', video)
    ) %>%
    pivot_longer(starts_with("k"), names_sep = "_", names_to = c("q", "ref")) %>%
    mutate(
        value = stringr::str_trim(tolower(value)),
        score = case_when(
            value == "don't know" ~ 0,
            value == "true" & ref == "T" ~ 1,
            value == "false" & ref == "F" ~ 1,
            value == "true" & ref == "F" ~ 0,
            value == "false" & ref == "T" ~ 0,
            otherwise ~ NA_real_
        )
    ) %>%
    select(-ref, -value) %>%
    pivot_wider(, names_from = q, values_from = score) %>%
    allot(d_)
```

## Data {.tabset}

### Demographics and ITT

> Who was assigned to treatment group will be in treatment group, regardless of
> the actual received treatment.

The two groups are comparable as there are no signigicant differences in
demographics. 

```{r demo_itt, results='asis'}
# d_ %<>% mutate(age = factor(age, levels = c('18-24', '25-34', ">35")))
# d_ %<>% mutate(age = as.numeric(age))
d_ %<>% mutate(edu = if_else(edu == "No formal education", "Primary school", edu))
d_ %<>% mutate(age = factor(age, c("18-24", "25-34", ">35")))
d_ %<>% mutate(nat = if_else(nat != "South African", 'Others', nat))
d_ %<>% mutate(across(c(edu, work, partner, momconnect,area), as.factor))

# d_ %>% tabstat(edu, momconnect)

rbind(
    d_ %>% tabstat(age, itt),
    d_ %>% tabstat(edu, itt),
    d_ %>% tabstat(area, itt),
    d_ %>% tabstat(race, itt),
    d_ %>% tabstat(nat, itt),
    d_ %>% tabstat(work, itt),
    d_ %>% tabstat(earn, itt),
    d_ %>% tabstat(partner, itt),
    d_ %>% tabstat(momconnect, itt)
) %>%
kable() %>%
    kable_classic(full_width = F, html_font = "Cambria") %>%
    add_header_above(c(" " = 1, "Video" = 2, " " = 1, " " = 1)) %>%
    pack_rows("Age", 1, 3) %>%
    pack_rows("Education", 4, 5) %>%
    pack_rows("Area", 6, 7) %>%
    pack_rows("Race", 8, 9) %>%
    pack_rows("Nationality", 10, 11) %>%
    pack_rows("Work", 12, 13) %>%
    pack_rows("Earning", 14, 16) %>%
    pack_rows("Partner", 17, 18) %>%
    pack_rows("MomConnect", 19, 20)
```

### Demographics and per-protocol

This shows that the two groups are comparable as there are no signigicant
differences in demographics. 

```{r demo_pp, results='asis'}
rbind(
    d_ %>% tabstat(age, pp),
    d_ %>% tabstat(edu, pp),
    d_ %>% tabstat(area, pp),
    d_ %>% tabstat(race, pp),
    d_ %>% tabstat(nat, pp),
    d_ %>% tabstat(work, pp),
    d_ %>% tabstat(earn, pp),
    d_ %>% tabstat(partner, pp),
    d_ %>% tabstat(momconnect, pp)
) %>%
kable() %>%
    kable_classic(full_width = F, html_font = "Cambria") %>%
    add_header_above(c(" " = 1, "Video" = 2, " " = 1, " " = 1)) %>%
    pack_rows("Age", 1, 3) %>%
    pack_rows("Education", 4, 5) %>%
    pack_rows("Area", 6, 7) %>%
    pack_rows("Race", 8, 9) %>%
    pack_rows("Nationality", 10, 11) %>%
    pack_rows("Work", 12, 13) %>%
    pack_rows("Earning", 14, 16) %>%
    pack_rows("Partner", 17, 18) %>%
    pack_rows("MomConnect", 19, 20)
```

### Scores distribution

There are 11 individuals with at least one missing questions, sensitivity will
be done using imputation to have the full data for analyses. The imputed data
including age, edu, work, partner, and all 28 knowledge questions.

```{r score_distribution, include=F}
d_ %>%
    mutate(score = rowSums(across(starts_with("k")))) %>%
    count(score) %>%
    kable()
```

Considering the total score distribution by variables one-by-one (univariate)

- Small increase in group with video intervention, both PP and ITT
classification, clearer increase in the ITT. 
- Age-group >35 have high score than others age-groups

```{r score_distribution_plot}
set.seed(2908)
dm <- mice::mice(d_, 10, print = F)
```

```{r plot_dist, fig.dim = c(7, 7)}
d5 <- complete(dm, 5) %>%
    mutate(score = rowSums(across(starts_with("k"))))

fpp <- d5 %>%
    ggplot(aes(factor(pp), score))  + geom_boxplot() +
    labs(x = "PP") + coord_flip()
fitt <- d5 %>%
    ggplot(aes(factor(itt), score))  + geom_boxplot() +
    labs(x = "ITT") + coord_flip()
fage <- d5 %>%
    ggplot(aes(factor(age), score))  + geom_boxplot() +
    labs(x = "ITT") + coord_flip()
fedu <- d5 %>%
    ggplot(aes(factor(edu), score))  + geom_boxplot() +
    labs(x = "edu") + coord_flip()
fwork <- d5 %>%
    ggplot(aes(factor(work), score))  + geom_boxplot() +
    labs(x = "work") + coord_flip()
fpartner <- d5 %>%
    ggplot(aes(factor(partner), score))  + geom_boxplot() +
    labs(x = "partner") + coord_flip()
fmom <- d5 %>%
    ggplot(aes(factor(momconnect), score))  + geom_boxplot() +
    labs(x = "Momconnect") + coord_flip()
farea <- d5 %>%
    ggplot(aes(factor(area), score))  + geom_boxplot() +
    labs(x = "Area") + coord_flip()
(fpp + fitt + fage + fedu) / (fwork + fpartner + fmom + farea)
```

## Count outcome {.tabset .tabset.pills}

### Best fit distribution

What distribution fit better to the data, if we assume it to be counts. Figure below shows that both Poisson and Negative Binomal are not a good fit. In this case, the upper bound is known (maximum is 28 correct answers), the `beta-binomial` can be used and showed to be a good fit.

```{r fitdit}
library(gamlss)

dm1 <- complete(dm, 1) %>%
    mutate(score = rowSums(across(starts_with("k"))), iid = id_)

x <- seq(10, 28, .5)
xi <- seq(10, 28, 1)

bb <- gamlss(y ~ 1, data = list(y = as.matrix(cbind(dm1$score, 28 - dm1$score))), family = BB)
bb <- dBB(x, plogis(bb$mu.coefficient), exp(bb$sigma.coefficient), bd = 28)

ps <- gamlss(y ~ 1, data = list(y = dm1$score), family = PO)
ps <- dPO(xi, exp(ps$mu.coefficient))

nb <- gamlss(y ~ 1, data = list(y = dm1$score), family = NBI)
nb <- dNBI(xi, exp(nb$mu.coefficient), exp(nb$sigma.coefficient) + 1e-6)

dm1 %>%
    ggplot(aes(score, fill = "Emprical dat")) +
    geom_density(alpha = .3) +
    coord_cartesian(expand = F) +
    geom_line(aes(score, dens, color = name), data = bind_rows(
        bind_cols(score = x, dens = bb, name = "Beta-binomial"),
        bind_cols(score = xi, dens = ps, name = "Poisson"),
        bind_cols(score = xi, dens = nb, name = "Negative-binomial")
    )) +
    labs(fill ='', y = "Score density (max 28)", title = "Empirical vs theoretical distr.") +
    theme(legend.position = 'bottom')
```

### Fitted model - beta_binomial

Follow the above results, we fit the model with beta-binomal distribution $score
\sim BB(n, \mu, \sigma)$ where $n=28$ for the total score, and the mean of the
distribution is $n\mu$.

```{r beta_binom, fig.dim = c(9, 4)}
library(brms)
n = 28
dm1 <- complete(dm, 1) %>%
    mutate(
        score = rowSums(across(starts_with("k"))),
        iid = id_, n = n
    )
tst <- brm(
    score | trials(n) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1,
    family = beta_binomial(),
    prior = c(
        set_prior("normal(0,3)", class = "Intercept"),
        set_prior("normal(0,3)", class = "b")
    #     # set_prior("cauchy(0,2)", class = "sd")
    ),
    # control = list(adapt_delta = 0.99),
    chains = 1, refresh = 0
)

lv <- c("b_ittYes", "b_age25M34", "b_age>35", "b_eduSecondaryandabove", "b_workYes", "b_partnerYes", "b_momconnectYes", "b_areaUrban")
lb <- c("Intervention", "Age - 25-34", "Age > 35", "Edu - Secondary+", "Working", "Have a partner", "Use MomConnect", "Urban")

fe <- tst %>%
    as_tibble() %>%
    apply(2, quantile, probs = c(.025, .25, .5, .75, .975)) %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    pivot_longer(-1) %>%
    pivot_wider(names_from = rowname, values_from = value) %>%
    filter(str_detect(name, "Intercept|phi|lp_|lprior", T)) %>%
    mutate(name = factor(name, lv, lb)) %>%
    ggplot(aes(name, `50%`)) +
    geom_hline(yintercept = 0, linetype = "dotted") +
    geom_linerange(aes(ymin = `2.5%`, ymax = `97.5%`)) +
    geom_linerange(aes(ymin = `25%`, ymax = `75%`), size = 1.5) +
    geom_point(shape = 21, fill = "grey90", size = 2) +
    coord_flip() +
    labs(
        title = "Estimated coefficients",
        x = "", y = "Coeficient (logit scale)"
    )

library('emmeans')
em <- emmeans(
    tst, list("itt", "age", "edu", "work", "partner", "momconnect", "area"),
    type = "response", offset = 0
)

lv <- c("itt", "age", "edu", "work", "partner", "momconnect", "area")
lb <- c("Intervention", "Age", "Education", "Working", "Have a partner", "Use MomConnect", "Area")

fi <- em %>%
    purrr::map(as_tibble) %>%
    bind_rows() %>%
    pivot_longer(c(itt, age, edu, work, partner, momconnect, area)) %>%
    drop_na() %>%
    mutate(name = factor(name, lv, lb)) %>%
    mutate(across(1:3, function(x) x * n)) %>%
    ggplot(aes(name, prob, ymin = lower.HPD, ymax = upper.HPD, color = value)) +
    geom_linerange(position = position_dodge2(.51)) +
    geom_point(position = position_dodge2(.51)) +
    geom_text(aes(y = upper.HPD+.21, label = value), position = position_dodge2(1), size = 3) +
    coord_flip() +
    guides(color = 'none') +
    labs(y = "Total score", x = '', title = "Estimated score")

fe + fi + plot_annotation(tag_levels = "A")
# plot.brmsfit(tst, plot = T, ask = F, combo = 'dens')
# brm_multiple()
```

### New subgroup from Maya

Remove questions `c(21, 23, 30, 32:35)`

```{r new_subgroup, fig.dim = c(9, 4)}
library(tidyselect)
remove_ls <- c(21, 23, 30, 32:35) %>% paste0("k", .)

n = 28 - length(remove_ls)

dm1 <- complete(dm, 1) %>%
    select(-remove_ls) %>%
    mutate(score = rowSums(across(starts_with("k"))), iid = id_, n = n)
    
tst <- brm(
    score | trials(n) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1,
    family = beta_binomial(),
    prior = c(
        set_prior("normal(0,3)", class = "Intercept"),
        set_prior("normal(0,3)", class = "b")
    ),
    chains = 1, refresh = 0
)

lv <- c( "b_ittYes", "b_age25M34", "b_age>35", "b_eduSecondaryandabove", "b_workYes", "b_partnerYes", "b_momconnectYes", "b_areaUrban" )
lb <- c( "Intervention", "Age - 25-34", "Age > 35", "Edu - Secondary+", "Working", "Have a partner", "Use MomConnect", "Urban" )

fe <- tst %>%
    as_tibble() %>%
    apply(2, quantile, probs = c(.025, .25, .5, .75, .975)) %>%
    as.data.frame() %>%
    rownames_to_column() %>%
    pivot_longer(-1) %>%
    pivot_wider(names_from = rowname, values_from = value) %>%
    filter(str_detect(name, "Intercept|phi|lp_|lprior", T)) %>%
    mutate(name = factor(name, lv, lb)) %>%
    ggplot(aes(name, `50%`)) +
    geom_hline(yintercept = 0, linetype = "dotted") +
    geom_linerange(aes(ymin = `2.5%`, ymax = `97.5%`)) +
    geom_linerange(aes(ymin = `25%`, ymax = `75%`), size = 1.5) +
    geom_point(shape = 21, fill = "grey90", size = 2) +
    coord_flip() +
    labs(
        title = "Estimated coefficients",
        x = "", y = "Coeficient (logit scale)"
    )

em <- emmeans(
    tst, list("itt", "age", "edu", "work", "partner", "momconnect", "area"),
    type = "response", offset = 0
)

lv <- c(
    "itt",
    "age",
    "edu",
    "work",
    "partner",
    "momconnect",
    "area"
)
lb <- c(
    "Intervention",
    "Age",
    "Education",
    "Working",
    "Have a partner",
    "Use MomConnect",
    "Area"
)

fi <- em %>%
    purrr::map(as_tibble) %>%
    bind_rows() %>%
    pivot_longer(c(itt, age, edu, work, partner, momconnect, area)) %>%
    drop_na() %>%
    mutate(name = factor(name, lv, lb)) %>%
    mutate(across(1:3, function(x) x * n)) %>%
    ggplot(aes(name, prob, ymin = lower.HPD, ymax = upper.HPD, color = value)) +
    geom_linerange(position = position_dodge2(.51)) +
    geom_point(position = position_dodge2(.51)) +
    geom_text(aes(y = upper.HPD+.21, label = value), position = position_dodge2(1), size = 3) +
    coord_flip() +
    guides(color = 'none') +
    labs(y = "Total score", x = '', title = "Estimated score")

fe + fi + plot_annotation(tag_levels = "A")
```

### Old subgroups - ITT

> Also removed questions `c(21, 23, 30, 32:35)`

```{r score_group}
select <- dplyr::select
complete(dm, 1) %>%
    pivot_longer(starts_with("k"), names_to = "q") %>%
    select(id_, q, value) %>%
    filter(!q %in% remove_ls) %>%
    left_join(cate, "q") %>%
    mutate(across(4:7, function(x) value * (x - 1))) %>%
    group_by(id_) %>%
    summarise(
        pc = sum(pc),
        bf = sum(bf),
        nc = sum(nc),
        bfnc = sum(bfnc)
    ) %>%
    allot(score_grp)

# find n
cate %>%
    filter(!q %in% remove_ls) %>%
    mutate(across(-1, function(x) sum(x == 2))) %>%
    select(-1) %>%
    head(1) %>%
    allot(n_sub)
```

```{r itt_subgroup, fig.dim = c(7, 5)}
complete(dm, 1) %>%
    left_join(score_grp, "id_") %>%
    mutate(
        npc = n_sub$pc,
        nbf = n_sub$bf,
        nnc = n_sub$nc,
        nbfnc = n_sub$bfnc
    ) %>%
    allot(dm1)

prio <- c(
    set_prior("normal(0,3)", class = "Intercept"),
    set_prior("normal(0,3)", class = "b")
)

mpc <- brm(
    pc | trials(npc) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1, family = beta_binomial(), chains = 1, prior = prio, refresh = 0
)
mbf <- brm(
    bf | trials(nbf) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1, family = beta_binomial(), chains = 1, prior = prio, refresh = 0
)
mnc <- brm(
    nc | trials(nnc) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1, family = beta_binomial(), chains = 1, prior = prio, refresh = 0
)
mbfnc <- brm(
    bfnc | trials(nbfnc) ~ itt + age + edu + work + partner + momconnect + area,
    data = dm1, family = beta_binomial(), chains = 1, prior = prio, refresh = 0
)

lv <- c("b_ittYes", "b_age25M34", "b_age>35", "b_eduSecondaryandabove", "b_workYes", "b_partnerYes", "b_momconnectYes", "b_areaUrban")
lb <- c("Intervention", "Age - 25-34", "Age > 35", "Edu - Secondary+", "Working", "Have a partner", "Use MomConnect", "Urban")

plot_e <- function(x) {
    x %>%
        as_tibble() %>%
        apply(2, quantile, probs = c(.025, .25, .5, .75, .975)) %>%
        as.data.frame() %>%
        rownames_to_column() %>%
        pivot_longer(-1) %>%
        pivot_wider(names_from = rowname, values_from = value) %>%
        filter(str_detect(name, "Intercept|phi|lp_|lprior", T)) %>%
        mutate(name = factor(name, lv, lb))
}

bind_rows(
    "Pregnancy care" = plot_e(mpc),
    "Breastfeed" = plot_e(mbf),
    "Newborn care" = plot_e(mnc),
    "Breastfeed & Newborn care" = plot_e(mbfnc),
    .id = "sub"
) %>%
    ggplot(aes(name, `50%`)) +
        geom_hline(yintercept = 0, linetype = "dotted") +
        geom_linerange(aes(ymin = `2.5%`, ymax = `97.5%`)) +
        geom_linerange(aes(ymin = `25%`, ymax = `75%`), size = 1.5) +
        geom_point(shape = 21, fill = "grey90", size = 2) +
        coord_flip() +
        facet_wrap(~sub) +
        labs(
            title = "Estimated coefficients",
            x = "", y = "Coeficient (logit scale)"
        )
```

